Large Language Models in Reinforcement Learning - A Comparison of Methods

### 2023-10-02 doc/paper.tex

Reinforcement Learning! And LLMs!

@@

\begin{IEEEkeywords}
\end{IEEEkeywords}

>>>>

Reinforcement Learning (RL) algorithms suffer when rewards are sparce and the state-action space is large. Even tasks which appear relatively simple can prove intractable if the completion of the task requires subtasks to be completed first, or if the reward only comes when the entire task has been completed. In such cases, random exploration is unlikely to lead the agent to discover a solution to the problem. The apparent simplicity of such problems is often due to human intuition, which allow us to quickly see possible solutions to a diverse set of problems. Large Language Models (LLMs) are trained on large corpura of human written text, and have been shown to capture parts of this intuition in many tasks \cite{sparks}. In recent years, LLMs have been succesfully used to aid RL agents in more efficient exploration, and have allowed them to solve problems which previous methods have been unable to \cite{omni} \cite{ellm}. We compare different methods for integrating an LLM into the deep learning reinforcement algorithm proximal policy optimization (PPO), and compare their efficiency against eachother. We find that BEST METHOD gives the best sample efficiency, outperforming normal PPO by PERCENTAGE in METRIC.

@@

\begin{IEEEkeywords}
large language models, reinforcement learning, minigrid, proximal policy optimization
\end{IEEEkeywords}
